### 2025-08-19 manuscript/manuscript.qmd
Revised analyses, added references, additions to MS

Equality – Why Should We Care?
Academia suffers from issues regarding equity. A lack equity impacts productivity, innovation, and job satisfaction in the workplace, which hugely impact academic progress. One aspect of this inequity is that gender. Women are more at a disadvantage than men, with evidence suggesting that women are less present in positions of power. For instance, in the UK, 24.6% of professors are women [@bhopal2021competing] when compared to the 44% of all grades in the academia [@harris2025gender]. A a pay gap remains between men and women in academia (female-male wage ratio 0.85 in 2020) [@quadlin2023higher]. In a “publish or perish” culture of science and academia [@kiai2019protect], one crucial aspect to focus on is authorship. The number and quality (e.g., journal reputation) of authorships an individual determines crucial career development such as grant funding and future (permanent) positions.

>>>>

Academia suffers from issues regarding equity. A lack equity impacts productivity, innovation, and job satisfaction in the workplace, which hugely impact academic progress. One aspect of this inequity is that gender. Women are more at a disadvantage than men, with evidence suggesting that women are less present in positions of power. For instance, in the UK in 2016-17, 24.6% of professors are women [@bhopal2021competing] when compared to the 44% of all grades in the UK academia [@harris2025gender]. Similar situation holds for italy [@Filandri03082021], 34% in the US [@huang2020]. A a pay gap remains between men and women in academia (female-male wage ratio of 0.85 in 2020 in the UK) [@quadlin2023higher]. In a “publish or perish” culture of science and academia [@kiai2019protect], one crucial aspect to focus on is authorship. The number and quality (e.g., journal reputation) of authorships an individual determines crucial career development such as grant funding and future (permanent) positions.
